BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-12-31 Paper2/BOAST.tex
conclusion

%%% Conclusion and Future Works %%%
\section{Conclusion and Future Works}

In this paper we presented the BOAST infrastructure as well as its application
to three use cases from the Mont-Blanc project. Results are encouraging as
BOAST proved to be a powerful and flexible tool that allowed gains in
performance compared to hand tuned codes. Performance portability of those
codes is also improved.

Future development will focus on three goals. Interfacing with binary analysis
tools like MAQAO~\cite{djoudi2005exploring} in order to build a feedback loop
to guide optimization. Interfacing with search space modellers/pruners in order
to optimize the search of the optimal version of a kernel. Work should also
continue on improving the support for vector codes. For instance producing a
collection of small to medium useful vector patterns (transposition, for
instance) in BOAST could really help users develop vectorized version of their
algorithm.

\section*{Acknowledgments}

>>>>

%%% CONCLUSION AND FUTURE WORKS %%%
\section{Conclusion and Future Works}

Application portability is an important issue that should be solved efficiently, especially given the large number of different processors now
available for today's supercomputers. The work needed to get performance portability is a tedious task, even for experienced programmers. The
availability of semi-automatic tools is therefore mandatory for the development of large simulation applications. Computing kernels' identification
and optimization has to be carefully performed as they usually consume most of the computing resources.

In this paper we presented the BOAST infrastructure (DLS and runtime) that aims at describing kernels in a high level language and allows the
comparison of the performance of different versions of the code in a simple and seamless way. We described its application to three use cases from the
Mont-Blanc project. Results are encouraging as BOAST proved to be a powerful and flexible tool that allowed gains in performance compared to hand
tuned codes. Performance portability of those codes is also improved.

Future development will focus on three main goals. First we find interesting to interface it with binary analysis tools like
MAQAO~\cite{djoudi2005exploring} in order to build a feedback loop to guide optimization. On the autotuning side, interfacing with search space
modellers/pruners in order to optimize the search of the optimal version of a kernel will allow us to gain some time in the optimization
process. Finally, work should also continue on improving the support for vector codes. For instance producing a collection of small to medium useful
vector patterns (transposition, for instance) in BOAST could really help users develop vectorized version of their algorithm. Other computing kernels
and applications will also be ported on various architectures.

%%% ACKNOWLEDGMENTS %%%
\section*{Acknowledgments}
